---
title: "Lab4"
author: "Siqi Fu, Yunran Chen, Lingxi Song"
date: "2019/10/21"
output: pdf_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r pkgs and read data}
library(dplyr)
library(ggplot2)
library(stringr)
library(corrplot)
library(tidyr)
badger=read.table("Badgers.txt",header = TRUE)
colnames(badger)=str_to_lower(colnames(badger))
badger=badger%>%
  mutate(farm=as.factor(farm_code_numeric))
```

#### Introduction
Management of badgers on Welsh and British farms triggers heated debate. Therefore, our aim of this project is to figure out factors related to the badger activity as well as to give estimates of farm-specific heterogeneity on badger activities. We have data from the surveys of 36 farms over three years and each farm is observed up to 8 seasons, which gives 273 observations altogether with predictor *year*,*season*,*no_active_setts_in_fields*,*accessible_feed_store_present*,*various types of crops*.etc and the primary outcome *signs_in_yard*. We will builed a Generalized Linear Mixed Effects Model for this topic because by intuition, we assume there is natural heterogeneity across different farms. 


#### EDA
```{r correlation, fig.cap="\\label{fig:cor} correlation summary plot",fig.width=5.5,fig.height=4}
badger_num = badger[,5:21]
corrplot(cor(badger_num),type = "upper",method = "ellipse", tl.cex = 0.4)
```

```{r fig.cap="\\label{fig:EDAnum} EDA for potenetial Variables",fig.width=5,fig.height=3.5}
# ggplot(badger %>% mutate(signs_in_yard=as.factor(signs_in_yard)), aes(no_active_setts_in_fields,no_buildings, color = signs_in_yard))+
#   geom_jitter() +
#   ggtitle("no_setts_in_fields vs. no_active_setts_in_fields, by color = signs_in_yard") +
#   theme_light()
ggplot(badger %>% select(signs_in_yard,no_active_setts_in_fields,no_setts_in_fields,no_buildings) %>% 
                  gather(key = "variables",value = "value",-signs_in_yard),
       aes(value,signs_in_yard))+geom_jitter()+ facet_wrap(~variables, scale = "free")+
   labs(title = "EDA for number of setts and buildings")+theme_bw()
```

```{r fig.cap="\\label{fig:EDAdummy} EDA for potenetial dummy variables"}
ggplot(badger %>% select(signs_in_yard,accessible_feed_store_present,accessible_cattle_house_present,
                         accessible_feed_present,grass_silage,cereal_silage,haystraw,
                         cereal_grains,concentrates,proteinblocks,sugarbeet,vegetables,molasses) %>% 
                  gather(key = "variables",value = "value",-signs_in_yard),
       aes(value,signs_in_yard))+geom_jitter()+ facet_wrap(~variables, scale = "free")+
   labs(title = "EDA for potential variables")+theme_bw()
```

## Modeling

```{r,model}
m1=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
```

```{r,diag for no_setts_in_fields}
m01 = glmer(signs_in_yard ~  no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
p1 = anova(m01,m1)[2,8]
p1

```

```{r, no_active_setts_in_fields}
m02 = glmer(signs_in_yard ~ no_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
p2 = anova(m02,m1)[2,8]
p2
```

```{r, no_buildings}
m03 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
        + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m03,m1)[2,8]
```

```{r, no_cattle_in_buidlings_yard}
m04 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings  
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m04,m1)[2,8]
```

```{r,accessible_feed_store_present}
m05 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m1,m05)[2,8]
```

```{r, accessible_cattle_house_present}
m06=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
        + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m1,m06)[2,8]
```

```{r, accessible_feed_present}
m07 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present           
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m1,m07)[2,8]
```

```{r, grass_silage}
m08 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
        + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m1,m08)[2,8]
```
```{r, cereal_silage}
m09 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m09,m1)[2,8]
```
```{r,haystraw}
m10 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
        + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage  + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m10,m1)[2,8]
```
```{r, cereal_grains}
m11 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
        + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw  +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m11,m1)[2,8]
```
```{r, concentrates}
m12=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains  + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m12,m1)[2,8]
```

```{r, proteinblocks}
m13 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m13,m1)[2,8]
```

```{r, sugarbeet}
m14 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks   + vegetables + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m14,m1)[2,8]
```

```{r, vegetables}
m15=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet  + molasses   
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m15,m1)[2,8]
```
```{r, molasses}
m16=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables    
         +  (1|farm_code_numeric) + (season|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m16,m1)[2,8]
```

```{r,farm_code}
m17 = glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
          + (season|year),
         family=binomial,data=badger,nAGQ=0)
anova(m1,m17)[2,8]
```

```{r,season}
m18=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) + (1|year),
         family=binomial,data=badger,nAGQ=0) 
anova(m18,m1)[2,8]
```

```{r,year}
m19=glmer(signs_in_yard ~ no_setts_in_fields+ no_active_setts_in_fields 
         +  no_buildings + no_cattle_in_buidlings_yard 
         + accessible_feed_store_present 
         + accessible_cattle_house_present + accessible_feed_present          
         + grass_silage + cereal_silage + haystraw + cereal_grains +
           concentrates + proteinblocks  + sugarbeet + vegetables + molasses   
         +  (1|farm_code_numeric) ,
         family=binomial,data=badger,nAGQ=0) 
anova(m1,m19)[2,8]
```

